Reionization Planck 2018 ...

### 2020-06-23 results/notes.tex

List of tests:\\
-

>>>>

List of tests:\\
\begin{itemize}
    \item {Direct MCMC chains
        \begin{enumerate}
            \item {PC zmax = 30}
            \item {PC zmax = 50}
            \item{tanh tau}
            \item{tanh highz model}
            \item{tanh highz model: fixed tau_lo, MCMC tau_hi ?}
        \end{enumerate}
    }

    \item {Direct MCMC chains}

\end{itemize}

\begin{figure}[t]
\includegraphics[width=0.40\textwidth]{results/cosmomc_runs/pl18_plots_zmax50/plot_pub_tau_gtz_dz_0p1_pl18_pc_zmax50_pliklite_post_and_pl18_pc_zmax50_pliklite_srollv2.pdf}
\caption{Comparing zmax = 50 PC chains using Planck 2018 original lowE vs srollv2 likelihood.
}
\label{fig:}
\end{figure}
